Response to the defense feedback

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Step 2: Address Recording}
Next, we record the memory access information based on the input
secret. We use the dynamic binary instrumentation (DBI) tool to record
whether a particular memory access information is accessed or
not. Inspired by AFL and Valgrind, we use a bitmap to represent
whether a particular memory is accessed or not. For example, the
bitmap ${0101}$ of address $l_1, l_2, l_3, l_4$ means that $l_2, l_4$
are hit during the execution. During the execution, the direct
information we get is the virtual memory address (VMA). However, we
transfer the address into the offset LMA (Load Memory Address) in
the original binary file. It has two benefits. First, modern computer
systems employ the Address Space Layout Randomization (ASLR). With
ASLR, the operating system randomly puts the code and data at
various memory offset. As a result, the code will get different
execution traces even for the same input because the image is
loaded at a different address each time. Second, it helps us find the
leakage site in the source code.

@@

There are two kinds of memory access: access to the code and access to the data. 
\begin{itemize}
\item Code Access. The memory address of the code is the value of the program counter $\mathit{rip}$ register. However, the length of x86 instructions can be from 1 byte to 15 bytes. For instructions whose length is longer than one byte, we also update the address after the value $\mathit{rip}$ until the address reaches the instruction's boundary.
\item Data Access. For instructions with memory access, we identify all the operands of each instruction. Same as the code addresses, the instruction can read or write multiple bytes one time.  Instructions like \textsf{push} and \textsf{pop} have implicit memory access. We all update the bitmap of the address correspondingly.
\end{itemize}

>>>>

\subsection{Step 2: Address Recording}
Next, we record the memory access information based on the input
secret. We use the dynamic binary instrumentation (DBI) tool to record
whether a particular memory access information is accessed or
not. Inspired by AFL and Valgrind, we use a bitmap to represent
whether a particular memory address is accessed or not. For example, the
bitmap ${0101}$ of address $l_1, l_2, l_3, l_4$ means that $l_2, l_4$
are hit during the execution. During the execution, the direct
information we get is the virtual memory address (VMA). However, we
transfer the address into the offset LMA (Load Memory Address) in
the original binary file. It has two benefits. First, modern computer
systems employ the Address Space Layout Randomization (ASLR). With
ASLR, the operating system randomly puts the code and data at
various memory offset. As a result, the code will get different
execution traces even for the same input because the image is
loaded at a different address each time. Second, it helps us locate the
leakage site in the source code.

@@

There are two kinds of memory access: access to the code and access to the data. 
\begin{itemize}
\item Code Access. The memory address of the code is the value of the program counter $\mathit{rip}$ register. However, the length of x86 instructions can be from 1 byte to 15 bytes. For instructions whose length is longer than one byte, we also update the address after the value $\mathit{rip}$ until the address reaches the instruction's boundary.
\item Data Access. For instructions with memory access, we identify all the operands of each instruction. Same as the code address, the instruction can read or write multiple bytes one time.  Instructions like \textsf{push} and \textsf{pop} have implicit memory accesses. We all update the bitmap of the address correspondingly.
\end{itemize}
